(Automatic) Speech Recognition Project --- Attacks on Neural Networks in a Lightweight Speech Pseudonymization Pipeline

### 2024-06-05 paper/paper.tex
Finished backdoor experiment

\section{Experiment}
% Specify the specific settings and individual attacks you performed.
  % Backdoor attack (JingleBack): poisoning rate, ...
  % Evasion attack (FGSM and PGD): ...

% Specify the transliteration and speaker you want the models to pick when they get the backdoor.

The code used for the experiments performed can be found at the following URL: \url{https://github.com/daanbrugmans/ru-automatic-speech-recognition-23-24}.

@@

\section{Results}

>>>>

\section{Experiment}
The code used for the experiments performed can be found at the following URL: \url{https://github.com/daanbrugmans/ru-automatic-speech-recognition-23-24}.

@@

\section{Results}
\begin{figure*}
    \centering
    \includegraphics[width=0.9\textwidth]{backdoor_metrics.png}
    \caption{An overview of the measured metrics for the JingleBack attack. Per poisoning rate, the Word Error Rate (WER), Word Error Rate Increase (WERI), Speaker Identification Accuracy (Acc), Attack Success Rate (ASR), and Clean Accuracy Drop (CAD) are given.}
    \label{fig:backdoor_metrics}
\end{figure*}
